\documentclass[a4paper]{report}
\usepackage{setspace}
%\usepackage{subfigure}

\pagestyle{plain}
\usepackage{amssymb,graphicx,color}
\usepackage{amsfonts}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage[a4paper, margin = 3cm, bottom = 2.5cm]{geometry}

\newtheorem{theorem}{THEOREM}
\newtheorem{lemma}[theorem]{LEMMA}
\newtheorem{corollary}[theorem]{COROLLARY}
\newtheorem{proposition}[theorem]{PROPOSITION}
\newtheorem{remark}[theorem]{REMARK}
\newtheorem{definition}[theorem]{DEFINITION}
\newtheorem{fact}[theorem]{FACT}

\newtheorem{problem}[theorem]{PROBLEM}
\newtheorem{exercise}[theorem]{EXERCISE}
\def \set#1{\{#1\} }

\newenvironment{proof}{
PROOF:
\begin{quotation}}{
$\Box$ \end{quotation}}



\newcommand{\nats}{\mbox{\( \mathbb N \)}}
\newcommand{\rat}{\mbox{\(\mathbb Q\)}}
\newcommand{\rats}{\mbox{\(\mathbb Q\)}}
\newcommand{\reals}{\mbox{\(\mathbb R\)}}
\newcommand{\ints}{\mbox{\(\mathbb Z\)}}

%%%%%%%%%%%%%%%%%%%%%%%%%%


\title{{\vspace{-14em}}\\
{{\Huge Project Title}}\\
{\large Optional Subtitle}\\}

\date{Submission date: 27 Jan 2020}
\author{Patrick (Daiqi) Wu\thanks{
{\bf Disclaimer:}
This report is submitted as part requirement for Patrick (Daiqi) Wu's BSc Computer Science degree at UCL. It is
substantially the result of my own work except where explicitly indicated in the text.
The report will be distributed to the internal and external examiners, but thereafter may not be copied or distributed except with permission from the author.}
\\ \\
BSc Computer Science\\ \\
Prof. Stephen Hailes and Phil Demetriou}



\begin{document}
 
\onehalfspacing
\maketitle
\begin{abstract}
Summarise your report concisely.
\end{abstract}
\tableofcontents
\setcounter{page}{1}


\chapter{Introduction}
This is just a bare minimum to get started.

\section{Section 1}
Chapters should contain numbered sections and sub-sections.

\subsection{Sub-Section 1}
Remember that this is a structured technical/academic report, not an essay.

\chapter{Background and Related Works}

\chapter{Requirement Gathering}

\chapter{Design and Implementation}

\chapter{Testing and Performance Evaluation}

\chapter{Conclusion and Future Work}

\section{More Content}

\section{Summary}

\chapter{Conclusions}

\section{Achievements}
Summarise the achievements to confirm the project goals have been met.
\section{Evaluation}
Evaluation of the work (this may be in a separate chapter if there is substantial evaluation).

\section{Future Work}
How the project might be continued, but don't give the impression you ran out of time!

\appendix


\chapter{Other appendices, e.g., code listing}
Put your appendix sections here

\end{document}